They're Clutching up! Team Momentum in Round-Based Esports

### 2022-08-13 paper/paper.tex
render a plot without error

Finally, I evaluate behavior when teams have two rounds left to win the
series, observing a peak in COD offensive win percentages in the 4-4
state, and no such oddity in Valorant.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, boxrule=0pt, breakable, interior hidden, frame hidden]}{\end{tcolorbox}}\fi

@@

{\centering

>>>>

Finally, I evaluate behavior when teams have two rounds left to win the
series, observing a peak in COD offensive win percentages in the 4-4
state, and no such oddity in Valorant.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, breakable]}{\end{tcolorbox}}\fi

@@
